### 2016-03-14 paper/conclusion.tex
another pass

\section{Conclusion and future directions}
We have proposed a novel MRF inference framework, Swarm Fusion, in
parallel computing environments. The framework is general and makes
popular inference techniques such as Alpha Expansion, Fusion Move,
Parallel Alpha Expansion, or Hierarchical Fusion, its special cases. Our
experiments have revealed that the framework exploits parallel
computational resources and achieves faster convergence, epseically for
challenging problems.  Our first future work is to conduct experiments
on cloud computing environments, in particular, the MapReduce
programming model, where the roles of mappers and reducers exactly
correspond to the processes of parallel multi-way fusion and solution
sharing, respectively.  Another future work is the automatic
configuration of the Swarm Fusion architecture.  Our experiments have
shown that optimal architectures are different for different problems.
An interesting direction is to adaptively change its architecture during
the computation, for example, switching to simple parallel
alpha-expansion for easy problems, or increasing the rate of solution
exchanges when solutions vary significantly across threads.
%
Parallel MRF inference has been a relatively under-explored topic in
Computer Vsion. Our idea is very simple, where adapting the Swarm Fusion
framework require minimal coding. We believe that this paper would
immediately benefit tens of thousands of Computer Vision researchers or
engineers in the world, who currently solve MRF problems. We will share
our source code and the datasets with the community.

>>>>

\section{Conclusion and future directions}
We have proposed a novel MRF inference framework, Swarm Fusion, in
parallel computing environments. The framework is general and makes
popular inference techniques such as Alpha Expansion, Fusion Move,
Parallel Alpha Expansion, and Hierarchical Fusion, its special cases. Our
experiments have revealed that the framework exploits parallel
computational resources and achieves faster convergence, epseically for
challenging problems.  Our first future work is to conduct experiments
on cloud computing environments, in particular, the MapReduce
programming model, where the roles of mappers and reducers exactly
correspond to the processes of parallel multi-way fusion and solution
sharing, respectively.  Another future work is the automatic
configuration of the Swarm Fusion architecture.  Our experiments have
shown that optimal architectures are different for different problems.
An interesting direction is to adaptively change its architecture during
the computation, for example, switching to simple parallel
alpha-expansion for easy problems, or increasing the rate of solution
exchanges when solutions vary significantly across threads.
%
Parallel MRF inference has been a relatively under-explored topic in
Computer Vsion. Our idea is very simple, where adapting the Swarm Fusion
framework require minimal coding. We believe that this paper would
immediately benefit tens of thousands of Computer Vision researchers or
engineers in the world, who currently solve MRF problems. We will share
our source code with the community.

### 2016-03-14 paper/optical_flow.tex
another pass

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
have been evaluated against the competing methods. The same
configurations as in the stereo problem have been used for optical flow,
that is, one iteration with ($\alpha=0, \beta=1$) in every 5 iterations and other iterations with ($\alpha=1, \beta=0$) for SF-MF, ($\alpha=3$, $\beta=0$) for SF-MF, and one iteration with ($\alpha=0, \beta=3$) in every 5 iterations and other iterations with ($\alpha=3, \beta=0$) for SF-MF.

>>>>

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
have been evaluated against the competing methods. For SF-MF, each thread repeats generating solution proposals ($\alpha=1, \beta=0$) for 4 iterations and fuses with one solution from others ($\alpha=0, \beta=1$) in one iteration. This pattern is repeated. For SF-SS, each thread always generates three solution proposals for fusion in each iteration ($\alpha=3$, $\beta=0$). For SF, the repeating pattern is ($\alpha=3, \beta=0$) for 4 iterations and ($\alpha=0, \beta=3$) for one iteration.

### 2016-03-14 paper/result_layered_depthmap.tex
another pass

We plot the energy minimization process in figure \ref{fig:layered_depthmap_convergence}. From the plot, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state. The reason is binary fusion of solution proposals (either from others or self) is too limited to contain a lower energy state due to the complexity of the problem itself. Only when multi-way fusion which explores much larger solution space is used (in FS-SS and FS), it becomes possible for the energy to further decrease. This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here. Note that FS also utilize multi-way fusion for solution sharing so that it performs better than FS-SS which has no solution sharing.

To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy minimization process in figure \ref{fig:layered_depthmap_by_alpha}. We can see that as the number of ways to fuse becomes larger, each fusion step takes longer time, but the chance of finding a lower energy state increases.

As shown in section \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different problem settings.

>>>>

We did our experiments on ours\_1 dataset in~\cite{layered_depthmap}. We plot the energy minimization process in figure \ref{fig:layered_depthmap_convergence}. From the plot, we can see that, Fusion Move, Parallel Fusion Move, and SF-MF all stalk at a high energy state. The reason is binary fusion of solution proposals (either from others or self) is too limited to contain a lower energy state due to the complexity of the problem itself. Only when multi-way fusion which explores much larger solution space is used (in SF-SS and SF), it becomes possible for the energy to further decrease. This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here. Note that SF also utilize multi-way fusion for solution sharing so that it performs better than SF-SS which has no solution sharing.

To further explore the effect of multi-way fusion, we use different $\alpha = {1, 3, 7, 15}$ in SF-SS model (disable solution sharing to better observe the effect of multi-way fusion) while keeping other parameters the same and plot the energy minimization process in figure \ref{fig:layered_depthmap_by_alpha}. We can see that as the number of ways to fuse becomes larger, each fusion step takes longer time, but the chance of finding a lower energy state increases.

### 2016-03-14 paper/result_optical_flow.tex
results
another pass

% \hang{figure file missing}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
  \caption{The energy minimization process for optical flow estimation of different methods. FS-MF has the best performance because of the solution sharing in early stage.}\label{fig:optical_flow_convergence}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_SF_MF_threads.png}
  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_PFM_threads.png}
  \caption{Per thread energy. The left and right figures show the energy minimization process on each working thread of our method in SF-MF configuration and parallel fusion move, respectively.}\label{fig:optical_flow_by_threads}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
  \caption{The energy minimization process for optical flow estimation with different $\beta$ values. Solution sharing generally makes energy minimization faster, but more solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
  \caption{The energy minimization process for optical flow estimation with different solution sharing frequency. Solution sharing generally makes energy minimization faster, but frequent solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}\label{fig:optical_flow_by_interval}
\end{figure}

Figure \ref{fig:optical_flow_convergence} illustrates the convergence rate of three competing methods (alpha expansion, parallel alpha expansion, hierarchical fusion) against
our swarm fusion method. From the figure we can observe that, both conducting binary fusion, FS-MF finds lower energy faster than PFM. This is because some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a lower energy quickly. Since there is no solution sharing in PFM model, other threads cannot share this lower energy state, and keeps working on its own state. On the other hand, FS-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share this lower energy state. To further demonstrate what is happening here, we plot per thread energy in PFM and FS-MF in figure \ref{fig:optical_flow_by_threads}. As we can see from the plots, in PFM model, one thread finds lower energy state faster than others, while other threads keep working at their own energy state. But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together. So there are more chance of finding effective proposals faster. Since the solution for optical flow can be locally improved by each thread, the final merging of PFM can effectively fuse good local results in different threads together and achieve a similar energy state with FS-MF model. But since FS-MF model shares information in the middle, a final merging becomes less necessary. Same comparison holds for FS-SS and FS. The multi-way fusion is ineffective in this problem setting since solution proposals are relatively independant and fusing multiple solutions together using TRW-S~\cite{TRW-S} is less efficient than fusing them one by one using~\cite{QPBO}.

They are two factors influencing solution sharing: 1) \textit{the number of solutions to share} and 2) \textit{the solution sharing frequency}. Both factors are controlled by $\beta$. As mentioned in the section \label{optical_flow}, we use $\beta = 1$ once in every five iterations and use $\beta = 0$ for all other iterations. This means we share one solution in every five iterations. To further understand the effect of solution sharing, we did two other experiments for comparison. In one experiment, we use $\beta = {0, 1, 2, 3}$ in every five iterations and $\beta = 0$ for other iterations (when $\beta = 0$, it is same with PFM without final merging). While keeping all other factor same, we plot the energy minimization process in figure \ref{fig:optical_flow_by_beta}. As shown in the figure, energy generally decreases faster with solution sharing. But since we need to perform one fusion for sharing each solution, sharing more solution decreases efficiency in this problem setting. While sharing multiple solutions might be useful in some other problem setting as it means each thread can get more global information early. In another experiment, we change the number of iterations between two consecutive solution sharing iterations (the number of zero $\beta$ between two non-zero $\beta$) and plot the energy minimization process in figure \ref{fig:optical_flow_by_interval}. From this figure, we can see that although solution sharing generally speeds up the optimization process, sharing solution too frequently is not a good practice. This is because when we share solution frequently, we have less time for generating and fusing new proposals. A good choice of the solution sharing frequency depends on specific problem setting.

>>>>

% \hang{figure file missing}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
  \caption{The energy minimization process for optical flow estimation of different methods. SF-MF has the best performance because of the solution sharing in early stage.}\label{fig:optical_flow_convergence}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_SF_MF_threads.png}
  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_PFM_threads.png}
  \caption{Per thread energy. The left and right figures show the energy minimization process on each working thread of our method in SF-MF configuration and parallel fusion move, respectively.}\label{fig:optical_flow_by_threads}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
  \caption{The energy minimization process for optical flow estimation with different $\beta$ values. Solution sharing generally makes energy minimization faster, but more solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
  \caption{The energy minimization process for optical flow estimation with different solution sharing frequency. Solution sharing generally makes energy minimization faster, but frequent solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}\label{fig:optical_flow_by_interval}
\end{figure}

We did our experiment on the Dimetrodon image pairs in the training set of Middlebury flow datasets~\cite{middlebury_flow}. Figure \ref{fig:optical_flow_convergence} illustrates the convergence rate of three competing methods (fusion move (FM), parallel fusion move (PFM), hierarchical fusion move (HFM)) against
our swarm fusion methods (SF-MF, SF-SS, SF). From the figure we can observe that, both conducting binary fusion, SF-MF finds lower energy faster than PFM. This is because some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a lower energy quickly. Since there is no solution sharing in PFM model, other threads cannot share this lower energy state, and keeps working on its own state. On the other hand, SF-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share information about this lower energy state. In this manner, all threads contribute to further decrease of this low energy state. To further demonstrate what is happening here, we plot per thread energy in PFM and SF-MF in figure \ref{fig:optical_flow_by_threads}. As we can see from the plots, in PFM model, one thread finds lower energy state faster than others, while other threads keep working at their own energy state. But in SF-MF model, all threads exchange information about the lowest energy state frequently and work on improving the lowest energy state together. Since the solution for optical flow can be locally improved by each thread, the final merging of PFM can effectively fuse good local results in different threads together and achieve a similar energy state with SF-MF model. But as SF-MF model shares information in the middle, a final merging becomes less necessary. Same comparison holds for SF-SS and SF. The multi-way fusion is inefficient in this problem setting since solution proposals are relatively independent and fusing multiple solutions together using TRW-S~\cite{TRW-S} is less efficient than fusing them one by one using~\cite{QPBO}.

They are two factors influencing solution sharing: 1) \textit{the number of solutions to share} and 2) \textit{the solution sharing frequency}. Both factors are controlled by $\beta$. As mentioned in the section \label{optical_flow}, we use $\beta = 1$ once in every five iterations ($\beta = 0$ for other iterations). This means we share one solution in every five iterations. To further understand the effect of solution sharing, we did two other experiments for comparison. In one experiment, we use $\beta = {0, 1, 2, 3}$ in every five iterations (when $\beta = 0$, it is same with PFM without final merging). While keeping all other factor same, we plot the energy minimization process in figure \ref{fig:optical_flow_by_beta}. As shown in the figure, energy generally decreases faster with solution sharing. But since we need to perform one fusion for sharing each solution, sharing more solution decreases efficiency in this problem setting. While sharing multiple solutions might be useful in some other problem setting as it means each thread can get more global information early. In another experiment, we change the number of iterations $k$ between two consecutive solution sharing iterations (the number of zero $\beta$ between two non-zero $\beta$) and plot the energy minimization process in figure \ref{fig:optical_flow_by_interval}. From this figure, we can see that although solution sharing generally speeds up the optimization process, sharing solution too frequently is not a good practice. This is because when we share solution frequently, we have less time for generating and fusing new proposals. A good choice of the solution sharing frequency depends on specific problem setting.
